Domain Tree Analysis

### 2017-08-24 domain_level/TextS4_domain_tree_analysis.Rmd
added in domain and trasnncript length data

A similar plot but in a different format
```{r}
norm_dom_counts <- counts(dds_dom, normalized=TRUE)
sigUp_norm_counts <- norm_dom_counts[rownames(norm_dom_counts) %in% rownames(resSigLFC),]

>>>>

A similar plot but in a different format
```{r}
domain_length_df <- fread("./data/domain_lengths.csv", data.table = FALSE)
domain_length_matrix <- matrix(domain_length_df[,2], ncol=1,
                               dimnames = list(row=domain_length_df[,1], col="len"))
rpkm_dom <- counts(dds_dom, normalized=FALSE)
dom_length_vector <- domain_length_matrix[rownames(rpkm_dom),]
domain_lib_size <- colSums(rpkm_dom)
rpkm_dom <- (t(t(rpkm_dom)/domain_lib_size)/dom_length_vector)*10^9
rpkm_dom <-  rpkm_dom[rownames(rpkm_dom) %in% rownames(resSigLFC),]

# norm_dom_counts <- counts(dds_dom, normalized=TRUE)
# sigUp_norm_counts <- norm_dom_counts[rownames(norm_dom_counts) %in% rownames(resSigLFC),]
# 
# percent_counts <- t(t(sigUp_norm_counts)/colSums(norm_dom_counts))

rpkm_dom <- rpkm_dom+1 #to deal with log transformation
sigUp_norm_counts_df <- melt(rpkm_dom)
colnames(sigUp_norm_counts_df) <- c("Domain Cluster", "Isolate", "RPKM")
sigUp_norm_counts_df$disease[grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"severe"
sigUp_norm_counts_df$disease[!grepl("^S.*",sigUp_norm_counts_df$Isolate)]<-"non-severe"
colnames(sigUp_norm_counts_df) <- c("Domain Cluster", "Isolate", "RPKM", "Phenotype")

gg <- ggplot(sigUp_norm_counts_df, aes(x=Phenotype, y=`RPKM`
                                       , colour=Phenotype))
gg <- gg + geom_boxplot(outlier.shape = NA, position = "dodge") + geom_jitter(width = 0.2, height = 0)
gg <- gg + facet_wrap(~`Domain Cluster`, nrow=1)
gg <- gg + scale_colour_manual(values = colors) + scale_y_log10()
gg <- gg + theme_bw()
gg
```
